### 2019-10-02 docs/ICTT2019/RMethod_ictt26_v2.tex
Journal and conference papers - tex, bibtex and figures
Journal and conference papers

%
% FIRST AUTHORS
%
\setlength{\baselineskip}{12pt}
\textbf{Daniele Tomatis}\\
DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\
daniele.tomatis@cea.fr\\
\vspace{0.25in}
\textbf{Roy Gross and Erez Gilad}\\
The Unit of Nuclear Engineering\\
Ben-Gurion University of the Negev, Israel\\
roygros@post.bgu.ac.il, gilade@bgu.ac.il\\
\end{center}

@@

\textcolor{magenta}{
	The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:
	\begin{equation}
	\label{eq:esc_prob_cyij-}
	\varepsilon^-_{i+1/2,j} = \frac{2}{r_{i+1/2}} 
	\displaystyle ~\int_0^{r_{i+1/2}} { dh\, y
		\int_0^{\ell_j}{ d\ell 
			\text{Ki}_2\left(\tau_{ji} + \sigma_j \ell \right)
		}
	} \,\, ,
	\end{equation}
	for $i<j$, where $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergo a collision. 
}

@@

Results in the cylindrical and spherical coordinate systems will be presented in the final version of the article.

>>>>

%
% FIRST AUTHORS
%
\setlength{\baselineskip}{12pt}
\textbf{Daniele Tomatis}\\
DEN, Service d'{\'e}tudes des r\'eacteurs et de math\'ematiques appliqu\'ees (SERMA),\\
CEA, Universit\'e Paris-Saclay, F-91191 Gif-sur-Yvette, France\\
daniele.tomatis@cea.fr\\
\vspace{0.25in}
\textbf{Roy Gross and Erez Gilad}\\
Unit of Nuclear Engineering\\
Ben-Gurion University of the Negev, Israel\\
roygros@post.bgu.ac.il, gilade@bgu.ac.il\\
\end{center}

@@

The corresponding form for the reduced escape probability for the incoming current is $\varepsilon^-_{i+1/2,j}$:

\textcolor{magenta}{
	\begin{equation}
	\label{eq:esc_prob_cyij-}
	\varepsilon^-_{i+1/2,j} = \frac{2}{r_{i+1/2}} 
	\displaystyle ~\int_0^{r_{i+1/2}} { dh\, y
		\int_0^{\ell_j}{ d\ell 
			\text{Ki}_2\left(\tau_{ji} + \sigma_j \ell \right)
		}
	} \,\, ,
	\end{equation}
	for $i<j$, where $\varepsilon^-_{i+1/2,j}\equiv 0$ for $i\geq j$ since in this case a neutron born in volume $j$ (or in volume $j=i$) cannot enter volume $i$ through its outer surface at radius $r_{i+1/2}$ without undergo a collision. 
}

@@

A one-group homogeneous problem is proposed hereafter in order to study the application of the Ronen method with angular redistribution in curvilinear geometries. Reference solutions are provided by collision probability method solvers, whose development take advantage of the implementation for the escape probabilities derived in section~\ref{sec:ce}. This choice is supported by the use of integral operators in the same Ronen method. Again, the implementation follows H\'ebert's textbook. The problems are solved in units of optical length, which means by simply setting the input total cross section equal to 1. The multiplying source becomes then $q = (c + \nu f) \phi_0 / 4\pi$, thus isotropic in angle, and with $c$ and $\nu f$ respectively as positive real numbers of secondaries per scattering and fission events. These numbers can be interpreted as conditional probabilities as well. The multiplicity $\nu$ acts as the eigenvalue of the problem. After the fundamental eigen-pair is known for given values of the constants and for a given size $L$, it is worthless to change $f$ alone to study the problem since only the product $\nu f$ counts for the balance (associated to the same eigenfunction). We choose then $f = 1$, ending up in only two free parameters for our study: $c_s$ and $L$. Even if this choice is unphysical for the assumed value of the total cross section together with $c > 0$, physical meaning is recovered by the fundamental value of $\nu$.

\textcolor{red}{Roy will be able to check these assertions in the coming days.}

\textcolor{blue}{The source assumes this form because the integration variables also have to the normalized by the mean free path (i.e. multiplied by the total cross section).}

\textcolor{green}{The use of the integral transport eqn. to get reference solutions is motivated by two main reasons. The first is to use again what we're implementing now for the escape probabilities. The second is to get the reference solution by inverting the operator used in the RM. So that we'll really know what is the solution to match. Furthermore, this won't be affected by ray effects of any kind. Lastly, we'll have to be very careful to the endpoint singularity when computing the collision probabilities.}
